Verifying Demonstrations

### 2019-12-03 paper/intro.tex
Renames DB-anon-cred to DB-Schnorr-UWB

\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security and formally verify it using 
Tamarin~\cite{TamarinDB}.

>>>>

\Cref{DB-Schnorr-UWB}, we present a new \ac{DB} version of the Schnorr protocol, 
different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security and formally verify it using 
Tamarin~\cite{TamarinDB}.
